---
title: "CLT Exponential Distribution Example"
author: "tbudd"
date: "December 19, 2015"
output: html_document
---
## Overview
[Expontential Distribution](https://en.wikipedia.org/wiki/Exponential_distribution)

## Simulations
1000 Simulations were run of the mean of 40 exponential distributions with lambda = 0.2

```{r}
set.seed(4321) ## set seed so this is reproducible
mns = NULL ## mns captures a vector of means; initialize to NULL
nosims = 1000 ## the number of simulations
lambda = 0.2
n = 40 ## sample size

## Get 1000 samples of the mean of 40 exponential distributions with lambda = 0.2
for (i in 1 : nosims) mns = c(mns, mean(rexp(n,lambda)))

```

## Sample Mean vs. Theoretical Mean
The theoretical mean of the mean of 40 distributions is the same as the mean of an exponential distribution, because of the Central Limit Theorem, so it is 1/lambda = 1/0.2 = 5.0.
The sample mean is calculated in the code chunk below and shown in Figure 1.
```{r kable,results='asis'}
library(knitr)
Parameter<-c("Exponential Mean","Theoretic Mean of Means", "Simulation Mean of Means")
Formula<-c("1/lamda","1/lambda","mean(means)")
Result<-c(1/lambda,1/lambda,mean(mns))
Fig1<-cbind(Parameter,Formula,Result)
kable(Fig1,caption="Figure 1: Mean of Means Calculations")
```

As can be seen in Figure 1, the simulation mean agrees closely with the theoretical mean of means. The sample mean is plotted on the histogram of the means of 40 exponential pdfs with lambda = 0.2 below in Figure 2.
```{r}
hist(mns,21,xlab="means",main="Figure 2: Histogram of 1000 Simulations of the Mean of 40 Exponentials")
abline(v = 5, col = "blue", lwd = 2)
```


## Sample Variance vs. Theoretical Variance
The variance of mean samples is the variance of the exponential distribution / the number of samples (the square of the standard error). The variance of the exponential is 1/lambda^2, so the theoretical variance of the mean of 40 means of exponentials is 1/(lambda^2*n) = 1/(0.2^2*40)=0.625.

The sample variance is calculated in the code chunk below and shown in Figure 3.
```{r}
Parameter<-c("Exponential Variance","Theoretic Variance of Means", "Simulation Variance of Means")
Formula<-c("1/lamda^2","1/(lambda^2*n)","variance(means)")
Result<-c(1/lambda^2,1/(lambda^2*n),var(mns))
Fig3<-cbind(Parameter,Formula,Result)
kable(Fig3,caption="Figure 3: Variation of Means Calculations")
```

As can been seen in Figure 3 above, the variance of the means from the simulation agrees well with the thoretical variance of means.

## Distribution
Plot the histogram of means of 40 exponential pdfs with lambda = 0.2
```{r}
hist(mns,21,xlab="means",main="Figure 4: Histogram of 1000 Simulations of the Mean of 40 Exponentials")
abline(v = 5, col = "blue", lwd = 2)
```
